---
title: "Lab 1"
author: "Gautam"
affiliation-title: "University of Utah"
date: last-modified
title-block-style: default
title-block-banner: true
format: 
  html:
      embed-resources: true
      theme: flatly
      code-block-bg: true
      code-block-border-left: "#31BAE9"
      highlight-style: printing
---

```{r setup}
#| include: false
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## What I want to learn this semester

My goal during the course is to learn the foundations and progress to more complicated visualization approaches. I anticipate acquiring expertise in tasks such as data import and cleaning, conducting comprehensive exploratory data analysis, and gaining proficiency with the ggplot2 package for crafting static visualizations. The basic objective is to navigate from basics to advanced skills, transforming raw data into insightful and visually compelling representations.

## Task 1

```{r task1}
# Put code here
data("mtcars")
filter_cars <- mtcars %>% filter(cyl == 6)
arrange_cars <- mtcars %>%arrange(desc(mpg))
my_cars <- mtcars %>% filter(mpg > 19)
```

## Task 2

```{r task2}
# Put code here
install.packages("jsonlite")
library(jsonlite)
#Added dataset from the internet
url <- "https://opendata.utah.gov/resource/5bsb-rb2f.json"
park_data <- fromJSON(url)

#Created aggregated Operation
grouped_data <- park_data %>%  group_by(park) %>%
  summarize(
    avg_acres = mean(acres)
  )

# Print the result
print(grouped_data)

```